Final Project Code ALL

### 2022-12-11 Draft_Final_Code.Rmd
Unsupervised Code Done

```{r}
ggplot(imdb_clean_clust, aes(x = hclust_num2, fill = Genre_1)) +
    geom_bar(position = "fill") +
    labs(x = "Cluster") + 
    theme_classic()

@@

ggplot(imdb_clean_clust, aes(x = Budget, y = Gross, color = hclust_num2)) +
  geom_point() +
  labs(x = "Budget in USD", 
       y = "Gross Profit in USD (Log Scale)", 
       title = "Visualizing Clusters: Gross Profit vs. Budget") + 
  theme_classic() + 
  theme(plot.title = element_text(size = 20, face = "bold"))

>>>>

```{r}
ggplot(imdb_clean_clust, aes(x = hclust_num2, fill = Genre_1)) +
  geom_bar(position = "fill") +
  labs(x = "Cluster", 
       y = "Proportion of Cluster", 
       title = "Selecting Number of Clusters (k)", 
       fill = "Genre 1") + 
  theme_classic() + 
  theme(plot.title = element_text(size = 20, face = "bold"))

@@

ggplot(imdb_clean_clust, aes(x = Budget, y = Gross, color = hclust_num2)) +
  geom_point() +
  labs(x = "Budget in USD", 
       y = "Gross Profit in USD (Log Scale)", 
       title = "Visualizing Clusters: Gross Profit vs. Budget",
       color = "Clusters") + 
  theme_classic() + 
  theme(plot.title = element_text(size = 20, face = "bold"))
